\section*{Committee}

\noindent \textbf{General Co-Chairs}

\begin{itemize}
  \item[] \member{Omar Ghattas}{University of Texas at Austin, USA}
  \item[] \member{Fiorella Sgallari}{University of Bologna}
\end{itemize}

\bigskip
\noindent \textbf{Scientific Committee}

\begin{itemize}
  \item[] \member{Marcelo Bertalm\'io}{University Pompeu Fabra, Spain}
  \item[] \member{Julianne Chung}{Virginia Tech., USA}
  \item[] \member{Per Christian Hansen}{Technical University of Denmark, Denmark }
  \item[] \member{Jari Kaipio}{University of Auckland, New Zealand}
  \item[] \member{Eric Miller}{Tufts University, USA}
  \item[] \member{Mila Nikolova}{CNRS ENS Cachan, France}
  \item[] \member{Ronny Ramlau}{Kepler University Linz, Austria and Johann Radon Institute, Austria}
  \item[] \member{Carola Sch\"{o}nlieb}{University of Cambridge, United Kingdom}
  \item[] \member{Gabriele Steidl}{Tech.Univ. Kaiserslautern, Germany}
  \item[] \member{Xue-Cheng Tai}{Hong Kong Baptist University, China }
  \item[] \member{Laura Waller}{University of California Berkeley, USA }
  \item[] \member{Brendt Wohlberg}{Los Alamos National Laboratory, USA}
\end{itemize}

\bigskip
\noindent\textbf{Organizing Committee}

\begin{itemize}
  \item[] \member{Carolina Beccari}{Dept. Mathematics, University of Bologna}
  \item[] \member{Giulio Casciola}{Dept. Mathematics, University of Bologna}
  \item[] \member{Salvatore Cuomo}{Dept. Mathematics and Applications ``Renato Caccioppoli'', University of Naples}
  \item[] \member{Luigi Di Stefano}{Dept. Computer Science and Engineering, University of Bologna}
  \item[] \member{Giovanni Dore}{Dept. Mathematics, University of Bologna}
  \item[] \member{Maurizio Falcone}{Dept. Mathematics, University of Roma ``La Sapienza''}
  \item[] \member{Luca Formaggia}{Department of Mathematics, Politecnico di Milano}
  \item[] \member{Patrizio Frosini}{Dept. Mathematics, University of Bologna}
  \item[] \member{Germana Landi,}{Dept. Mathematics, University of Bologna}
  \item[] \member{Alessandro Lanza}{Dept. Mathematics, University of Bologna}
  \item[] \member{Damiana Lazzaro}{Dept. Mathematics, University of Bologna}
  \item[] \member{Roberto Mecca}{University of Bologna and University of Cambridge}
  \item[] \member{Serena Morigi}{Dept. Mathematics, University of Bologna}
  \item[] \member{Michele Piana}{Dept. Mathematics, University of Genova}
  \item[] \member{Elena Loli Piccolomini}{Dept. Mathematics, University of Bologna}
  \item[] \member{Giulia Scalet}{Dept. Civil Engineering and Architecture, University of Pavia}
  \item[] \member{Federica Sciacchitano}{Dept. Mathematics, University of Genova}
  \item[] \member{Valeria Simoncini}{Dept. Mathematics, University of Bologna}
  \item[] \member{Giulia Spaletta}{Dept. Mathematics, University of Bologna}
  \item[] \member{Fabiana Zama}{Dept. Mathematics, University of Bologna}
\end{itemize}

