\newpage

%-----Registration Desk
\gisection{Registration Desk}
\addcontentsline{toc}{section}{Registration Desk}
The registration desk is located in the hall of Building A (via B. Andreatta 8) and is open during the following hours:

\bigskip

\begin{tabular}{r l }
      Monday, June 4: & 15:00 -- 18:30 \\
     Tuesday, June 5: & 11:30 -- 18:30 \\
   Wednesday, June 6: & 08:00 -- 18:30 \\
    Thursday, June 7: & 08:00 -- 13:30 \\
      Friday, June 8: & 08:00 -- 13:30 \\
\end{tabular}

%-----Badges
\gisection{Badges} 
Carry your badge during the conference so that you can be admitted to all technical sessions, coffee breaks, lunches, reception and banquet.\\
\textbf{Emergency numbers} are provided on the back of your name badge! 

%-----Registration Fee Includes
\gisection{Registration Fee Includes}

\bigskip

\begin{itemize}
  \item Admission to all technical sessions
  \item Business Meeting (open to SIAG/IS members)
  \item Social dinner (Wednesday)
  \item Coffee breaks 
  \item Welcome lunch (Tuesday)
  \item Welcome cocktail during the evening Poster Session (Tuesday)
  \item Room set-ups and audio/visual equipment
  \item Wi-Fi access at the conference
\end{itemize}%-----Conference Talk Arrangements

%-----Conference Talk Arrangements

\gisection{Conference Talk Arrangements}

\noindent All \textbf{plenary talks} will have a slot of 45 minutes
(5 minutes reserved for questions and discussion included).\\\\
The \textbf{minitutorials} will last 2 hours.\\\\
All \textbf{minisymposia talks} will have a slot of 30 minutes (5 minutes reserved for questions and discussion included).\\
All \textbf{contributed talks} will last 20 minutes (5 minutes reserved for questions and discussion included).\\\\
If you need to copy your presentation slides from your USB flash drive to a computer in lecture hall or meeting room, please do it in advance before
the session starts.

%-----Important Notice to Poster Presenters
\gisection{Important Notice to Poster Presenters}

\noindent The \textbf{poster sessions} are scheduled:
\begin{center}
  \textbf{Tuesday, June 5} \\
  from 18:30 onwards \\
  in Building A and B\\
  with Welcome cocktail

  \bigskip
   
  \textbf{Wednesday, June 6} \\
  from 11:30 to 13:00 \\
  in Building A and B
\end{center}

\noindent The \textbf{Best Poster Award} will be given on Friday, June 8 at 13:00 in Building A, Room A.\\

\noindent All posters participating to the Best Poster Award are available on the Conference website from June 1.\\
Poster presenters are requested to set up
their material on the provided poster boards (70 cm x 100 cm), following the instructions in the participant folder and be present during both sessions.  
All materials must be posted by Tuesday, June 5 at 18:00.
The conference is not responsible for discarded posters.

%------------Wi-Fi Access
\gisection{Wi-Fi Access}

The username and password of your account during the conference period (5-8 June) can be found in your folder.

The users of an institution belonging to \href{https://www.eduroam.org/}{EduRoam} are able to use the local wireless network using their own credentials (username and password).

%-------------------Standard Audio/VIsual Set-Up in Meeting Rooms
\gisection{Standard Audio/Visual Set-Up in Meeting Rooms}
The plenary session room has a PC, two screens and two data projectors.\\ 
All other concurrent/breakout rooms have a PC, a screen, a data projector and a whiteboard (overhead projectors are also available).\\
The data projectors support VGA connection only. Presenters requiring an HDMI or alternate connection must provide their own adaptor.\\
Cables or adaptors for Apple computers are not supplied, as they vary for each model: please bring your own cable/adaptor if using a Mac computer. 
The conference is not responsible for the safety and security of speakers' computers.

%-------------Recording of presentations
\gisection{Presentations Recording}
During the conference audio and video recording is prohibited without the written permission of the speaker and the conference organizers.

%-------------SIAM Books and Journal
\gisection{SIAM Books and Journals}

\noindent Display copies of selected SIAM books are available on site.

\bigskip

\noindent SIAM books are offered at \textbf{discounted prices} for all attendees. 
SIAM members can apply their member discount, and all attendees are entitled to a 20\% Conference Discount.

\bigskip

\noindent The SIAM \textbf{book table} will be staffed from 9:00 through 17:30. 
The book table will close at 16:00 on Friday. 
If the SIAM book table is temporarily unattended, please take a copy of the Titles on Display to order online and receive the Conference Discount. 
\textit{(Note: all prices in the Titles on Display are in Euros.)}

\gisection{Table Top Displays}

\begin{itemize}
  \item SIAM: Building A, second floor
  \item IOP: Buiding A, first floor
  \item Springer Nature: Building A, first floor
\end{itemize}

%------------------ GET TOGETHERS
\addcontentsline{toc}{section}{Get-togethers}
\gisection{Get-togethers}

\subsection*{Tuesday, June 5}

\begin{itemize}
  \item[] 11:45 -- 13:30, Welcome lunch
  \item[] 18:30 -- 20:30, Poster Session I and Welcome cocktail
\end{itemize}

\subsection*{Wednesday, June 6}

\begin{itemize}
  \item[] 11:30 -- 13:00, Poster Session II
  \item[] 17:45 -- 18:30, Business Meeting (open to SIAG/IS members)
  \item[] 20:00 Social dinner
\end{itemize}

%---------------Lunches
\newpage % PIETRO FIXME
\gisection{Lunches}
There are multiple options for your lunches on Wednesday, Thursday and Friday. 
\bigskip
\begin{itemize}
  \item Two different \textbf{lunch boxes} prepared by the catering in the conference location: it can be ordered at the coffee desk the day before.
  \item The John Hopkins University canteen in front of the conference location: Please show your conference badge.
  \item Elior canteen, Piazza Vittorio Puntoni 1: Special rates for the conference participants.
\end{itemize}
\bigskip
Several bars and restaurants are available for lunch in the area surrounding via Andreatta and via Belmeloro: The complete list is in your folder.

%---------------Conference Banquet
\gisection{Conference Banquets}
The \textbf{Conference banquet} will be served in Palazzo Re Enzo, Piazza del Nettuno 1C. Please carry your badge and ticket with you for admission. For security
reasons, only 650 persons are admitted. So a second \textbf{special dinner} is organized in the same evening at Cantina Bentivoglio, via Mascarella 4 with 
Jazz music.

\bigskip 

\noindent Additional conference banquet \textbf{tickets} are available at the price of 65 euros. 
Please purchase it at the registration desk before Tuesday, June 5 afternoon.\\

%---------------Child Care
\gisection{Child Care}
\subsection*{Le cicogne} 
Typical rates: if reserved a few days in advance: \euro 16 / each hour (for a maximum of 2-3-4 hours) for a basic baby sitting 
and \euro 20 / each hour for a baby sitter speaking foreign languages.
If requested one day before: \euro 18 + hourly rate.
If requested the same day: \euro 28 + hourly rate.

\smallskip\noindent website: \href{http://www.lecicogne.net}{http://www.lecicogne.net}

\subsection*{Born to life}
Typical rates: \euro 25 agency fee + hourly rate \euro 13. After 22:00: \euro 15. Foreign languages available. Reservations: 2 weeks in advance.

\smallskip\noindent website: \href{http://www.bolognababysitter.it}{http://www.bolognababysitter.it}

\gisection{General information in Bologna}

\begin{itemize}
  \item Emergency Phone Number: 118 Medical Emergencies; 113 Emergency Police Help Number; 115 Fire Department 
  \item Time Zone: CEST (Central European Summer Time); UTC/GMT+2
  \item Electricity: 220 V, 50Hz; power sockets follow European standards;
  \item Currency: Euro (EUR)
  \item Dial Country Code: +39
  \item Working hours Banks: 8:30 -- 13:30; 14:30 -- 15:45 (Monday to Friday) 
  \item Buses in Bologna: visit \href{https://www.tper.it/ }{www.tper.it}
  \item Pharmacies: 08:30 -- 12:30, 15:30 -- 19:30 (Monday to Saturday, some are open 24 hours a day, everyday) 
  \item Shops: 9:30 -- 13:00; 15:30 - 19:30 (Monday to Saturday) 
  \item Bologna Touristic Bureau: \href{https://www.bolognawelcome.com/en}{www.bolognawelcome.com/en}
\end{itemize}

%---------------Please Note
\gisection{Please note}
The conference is not responsible for the safety and security of participants' computers. 
Do not leave your laptop computers and personal belongings unattended. 
Please remember to turn off your mobile during all the sessions.\\\\ 
The conference cannot provide photocopying and dollar exchange service. 
A bank can be found in piazza Aldrovandi 12/A (opening hours: 8:20 -- 13:20 and 14:30 -- 16:00).

%---------------Comments
\gisection{Comments?}
Comments about SIAM IS18 are encouraged! Please send it to Cynthia Phillips, SIAM Vice President for Programs (vpp@siam.org).
